Optimal (Multiway) Spatial Joins

### 2024-05-28 msj.tex
yufei

\extraspacing {\underline{\em Example 4.6.}} It is clear from Figure~\ref{fig:hv:type1:ex}d that $\cross_H(\alpha^*)$ contains $h_2, h_4$, and $h_5$, sorted in ascending order of y-coordinate. Recall that 
$\gbot(\bm{t}_1) = \gbot(\bm{t}_2) = \alpha'$. Both $\dcross_H(\bm{t}_1) = \set{h_2}$ and $\dcross_H(\bm{t}_2) = \set{h_2, h_4, h_5}$ are prefixes of the sorted list.
\qed

@@

\noindent {\underline{\em Example 5.2.}} In Figure~\ref{fig:guard}a, segment $h_1$ has no left-covering rectangle in $R_2$ and thus has no trimmed segment. Segment $h_2$ has one left-covering rectangle in $R_2$, which is $\beta_1$. As the entire $h_2$ is covered by $\beta_1$, it is equivalent to its trimmed segment $h_2'$; see Figure~\ref{fig:hv:type2:ex}b. Segment $h_3$ has two left-covering rectangles in $R_2$, which are $\beta_2$ and $\beta_3$. The right endpoint of its trimmed segment $h_3'$, as shown in Figure~\ref{fig:guard}b, is decided by the right edge of $\beta_3$. Therefore, $H' = \set{h_2', h_3'}$. It is clear from Figure~\ref{fig:guard}b that $\J(R_1, H', V)$ has 3 tuples: $\bm{t}_1 = (\alpha, h_2', v_1), \bm{t}_2 = (\alpha, h_3', v_1)$, and $\bm{t}_3 = (\alpha, h_3', v_2)$.
\qed

@@

\extraspacing {\underline{\em Example 5.4.}} For $\bm{t}_1 = (\alpha, h_2', v_1)$, first find the full segment of $h_2'$, which is $h_2$. As $\beta_1$ is the only rectangle in $\contained_{R_2}(\bm{t}_1)$, Line 5 adds tuple $(\alpha, \beta_1, h_2, v_1)$ to $\J_2$. For $\bm{t}_2 = (\alpha, h_3', v_1)$, the full segment of $h_3'$ is $h_3$. As $\contained_{R_2}(\bm{t}_2) = \set{\beta_1, \beta_2, \beta_3}$, Line 5 adds $(\alpha, \beta_1, h_3, v_1)$, $(\alpha, \beta_2, h_3, v_1)$, and $(\alpha, \beta_3, h_3, v_1)$ to $\J_2$. Finally, the processing of $\bm{t}_3 = (\alpha, h_3', v_2)$ adds $(\alpha, \beta_3, h_3, v_2)$ to $\J_2$.
\qed

@@

\extraspacing {\underline{\em Example 5.5.}} As mentioned $\J(R_1, H', V)$ has 3 tuples $\bm{t}_1$, $\bm{t}_2$, and $\bm{t}_3$. Both $\bm{t}_2 = (\alpha, h_3', v_2)$ and $\bm{t}_3 = (\alpha, h_3', v_2)$ have $h_3'$ as the horizontal segment. Therefore, $\minleft(h_3')$ equals the smaller between the x-coordinate of $v_1$ and that of $v_2$. The minimal segment $h_3^*$ of $h_3'$ is shown in Figure~\ref{fig:hv:type2:ex}(c). On the other hand, it is easy to verify that $\minleft(h_2')$ is the x-coordinate of $v_1$. The minimal segment $h_2^*$ of $h_2'$ is also shown in Figure~\ref{fig:hv:type2:ex}(c).
\qed

>>>>

\extraspacing {\underline{\em Example 4.6.}} It is clear from Figure~\ref{fig:hv:type1:ex}d that $\cross_H(\alpha^*)$ contains $h_2, h_4$, and $h_5$, sorted in ascending order of y-coordinate. Recall that 
$\gbot(\bm{t}_1) = \gbot(\bm{t}_2) = \alpha'$. Both $\dcross_H(\bm{t}_1) = \set{h_2}$ and $\dcross_H(\bm{t}_2) = \set{h_2, h_4, h_5}$ are prefixes of the sorted list, as is consistent with Lemma~\ref{lmm:hv:type1:cross-r*}.
\qed

@@

\noindent {\underline{\em Example 5.2.}} Segment $h_1$ has no left-covering rectangle in $R_2$ (see Figure~\ref{fig:guard}a) and thus has no trimmed segment. Segment $h_2$ has one left-covering rectangle in $R_2$, which is $\beta_1$. As the entire $h_2$ is covered by $\beta_1$, it is equivalent to its trimmed segment $h_2'$; see Figure~\ref{fig:hv:type2:ex}b. Segment $h_3$ has two left-covering rectangles in $R_2$, which are $\beta_2$ and $\beta_3$. The right endpoint of its trimmed segment $h_3'$, as shown in Figure~\ref{fig:guard}b, is decided by the right edge of $\beta_3$. Therefore, $H' = \set{h_2', h_3'}$. It is clear from Figure~\ref{fig:guard}b that $\J(R_1, H', V)$ has 3 tuples: $\bm{t}_1 = (\alpha, h_2', v_1), \bm{t}_2 = (\alpha, h_3', v_1)$, and $\bm{t}_3 = (\alpha, h_3', v_2)$.
\qed

@@

\extraspacing {\underline{\em Example 5.4.}} For $\bm{t}_1 = (\alpha, h_2', v_1)$, first find the full segment of $h_2'$, which is $h_2$. As $\beta_1$ is the only rectangle in $\contained_{R_2}(\bm{t}_1)$, Line 5 of the algorithm adds tuple $(\alpha, \beta_1, h_2, v_1)$ to $\J_2$. For $\bm{t}_2 = (\alpha, h_3', v_1)$, the full segment of $h_3'$ is $h_3$. As $\contained_{R_2}(\bm{t}_2) = \set{\beta_1, \beta_2, \beta_3}$, Line 5 adds $(\alpha, \beta_1, h_3, v_1)$, $(\alpha, \beta_2, h_3, v_1)$, and $(\alpha, \beta_3, h_3, v_1)$ to $\J_2$. Finally, the processing of $\bm{t}_3 = (\alpha, h_3', v_2)$ adds $(\alpha, \beta_3, h_3, v_2)$ to $\J_2$.
\qed

@@

\extraspacing {\underline{\em Example 5.5.}} As mentioned, $\J(R_1, H', V)$ has 3 tuples $\bm{t}_1$, $\bm{t}_2$, and $\bm{t}_3$. Both $\bm{t}_2 = (\alpha, h_3', v_1)$ and $\bm{t}_3 = (\alpha, h_3', v_2)$ have $h_3'$ as the horizontal segment. Therefore, $\minleft(h_3')$ equals the smaller between the x-coordinate of $v_1$ and that of $v_2$. The minimal segment $h_3^*$ of $h_3'$ is shown in Figure~\ref{fig:hv:type2:ex}(c). On the other hand, it is easy to verify that $\minleft(h_2')$ is the x-coordinate of $v_1$. The minimal segment $h_2^*$ of $h_2'$ is also shown in Figure~\ref{fig:hv:type2:ex}(c).
\qed
